Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-12-05 dsn-2018/bare_conf.tex
Referenced figure of transition states
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

@@

\begin{figure*}
\begin{center}
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{Figs/differential-1289.png}
    \caption{Collision 1289}
    \label{Fig:1289}
  \end{subfigure}\\
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{Figs/differential-1250.png}
    \caption{Collision 1250}
    \label{Fig:1250}
  \end{subfigure}\\
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{Figs/transitions.pdf}
    \caption{Differential Path Transitions}
    \label{Fig:Transitions}
  \end{subfigure}\\
\end{center}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{Figs/differential-1289.png}
    \caption{Collision Class S1289}
    \label{Fig:1289}
  \end{subfigure}\\
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{Figs/differential-1250.png}
    \caption{Collision Class S1250}
    \label{Fig:1250}
  \end{subfigure}\\
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{Figs/transitions.pdf}
    \caption{Differential Path Transitions between S1289 and S1250}
    \label{Fig:Transitions}
  \end{subfigure}\\
  \caption{An optimal path between collision classes S1289 and S1250,
  centered around S0 (M. Schl{\"a}ffer's Collision Class), showing each
  intermediate collision class, transition steps, and appropriate
  round differences.}
  \label{Fig:Transition}
\end{center}
\end{figure*}

An example of this intuition can be seen in Figure \ref{Fig:Transition}.
From M. Schl{\"a}ffer's collision class, S1289 and S1250 are equidistant, with
$\delta(C_{Schlaffer}, S1289) = 3$ and $\delta(S1289, S1250) = 3$.
Individual step transitions between $S1289$ and $S1250$ are notated in
Figure \ref{Fig:Transitions}, showing each step and each intermediate collision
class. Figures \ref{Fig:1289} and \ref{Fig:1250} show the complete differential
path for S1289 and S1250 respectively.

By considering paths among neighbors, a more optimal exploration strategy can
be constructed, favoring switching rounds before exploring cliques when the
triangle inequality holds in the local search area. This allows for a wider
coverage in differential paths, escaping the local collision type, and
ultimately improving chosen prefix and second preimage attacks.

@@
